### 2019-03-19 draft_charts.Rmd
Chnages before meeting with Alice.

```{r rmarkdown-setup, echo = FALSE}
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

@@

library(tidyverse)
library(urbnthemes)

@@

read_csv("data/figure1.csv") %>%
  filter(ncharts_reprate %in% c("0-50%", "50-75%")) %>%
  filter(doby %in% cohorts) %>%
  group_by(doby) %>%
  summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>%
  ggplot(aes(doby, rep_rate_threshold)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::percent(rep_rate_threshold / 100)), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1))) +
  labs(title = "Age 70 Percentage of People Who Fail to Replace 75% of Age 50-59 Earnings",
       x = "Birth cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()   
```

@@

```{r chart2}
read_csv("data/figure2.csv") %>%
  filter(doby %in% cohorts) %>%
  ggplot(aes(doby, ncharts_aftertax_income_P50)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::dollar(ncharts_aftertax_income_P50, largest_with_cents = 0)), 
            vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1))) +
  labs(title = "Age-70, per-capita, price-adjusted income",
       subtitle = "Median shared annuitized income with imputed rent, other income, and taxes",
       x = "Birth cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()
```

@@

```{r chart3}
read_csv("data/figure3.csv") %>%
  filter(doby %in% cohorts) %>%
  ggplot(aes(doby, ncharts_aftertax_income_P50, fill = male)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::dollar(ncharts_aftertax_income_P50, largest_with_cents = 0)), 
            position = position_dodge(width = 0.7), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15))) +
  labs(title = "Age-70, per-capita, price-adjusted, shared annuitized income with imputed rent, other income, and taxes",
       subtitle = "By sex",
       x = "Birth cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis() 
```

@@

```{r, chart3b}
read_csv("data/figure3b.csv") %>%
  filter(doby %in% cohorts) %>%
  ggplot(aes(doby, Ownssb_P50, fill = male)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::dollar(Ownssb_P50, largest_with_cents = 0)), 
            position = position_dodge(width = 0.7), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15))) +
  labs(title = "Median Age-70 Price-Adjusted Social Security Benefits by Sex",
       x = "Birth cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis() 
```

@@

```{r chart4}
read_csv("data/figure4.csv") %>%
  filter(doby %in% cohorts) %>%
  filter(!is.na(male)) %>%
  ggplot(aes(doby, lifetime_earn_P50, fill = male)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::dollar(lifetime_earn_P50, largest_with_cents = 0)), 
            position = position_dodge(width = 0.7), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15))) +
  labs(title = "Median Price-adjusted Earnings from Ages 25 to 69 at Age 70",
       subtitle = "By sex",
       x = "Birth cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis() 
```

@@

```{r chart5}
benefits <- c("Worker only", "Worker supplemented by spousal or survivor", "Spouse or survivor only")

read_csv("data/figure5.csv") %>%
  filter(doby %in% cohorts) %>%
  select(doby,
         `Worker supplemented by spousal or survivor` = dualben_Mean,
         `Worker only` = wrkonly_Mean,
         `Spouse or survivor only` = auxonly_Mean) %>%
  gather(key = "benefit_type", value = "share", -doby) %>%
  mutate(benefit_type = factor(benefit_type, levels = benefits)) %>%
  ggplot(aes(benefit_type, share, fill = doby)) +
  geom_col(position = "dodge") +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)), labels = scales::percent_format(accuracy = 1)) +
  labs(title = "Social Security Benefit Type at Age 70 for Female Beneficiaries (%)",
       x = NULL,
       y = NULL) +
  remove_ticks()
```

@@

```{r chart6}
read_csv("data/figure6.csv") %>%
  filter(doby %in% cohorts) %>%
  filter(!is.na(raceeth)) %>%
  filter(raceeth != "4.Other") %>%
  ggplot(aes(doby, ncharts_aftertax_income_P50, fill = raceeth)) +
  geom_col(position = "dodge") +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15)), 
                     labels = scales::dollar) +
  labs(title = "Age-70, per-capita, price-adjusted, shared annuitized income\nwith imputed rent, other income, and taxes",
       subtitle = "By race and ethnicity",
       x = "Birth cohort",
       y = NULL) +
  remove_ticks()
```

@@

```{r chart8}
read_csv("data/figure8.csv") %>%
  filter(doby %in% cohorts) %>%
  select(doby,
         `Scheduled law` = PCssb_P50,
         `Payable benefits` = PCssb_payable_P50) %>%
  gather(key = "Benefit type", value = "benefit", -doby) %>%
  mutate(`Benefit type` = factor(`Benefit type`, levels = c("Scheduled law", "Payable benefits"))) %>%
  ggplot(aes(doby, benefit, fill = `Benefit type`)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::dollar(benefit, largest_with_cents = 0)), 
            vjust = -1,
             position = position_dodge(width = 0.8)) +   
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15)), 
                     labels = scales::dollar) +
  labs(title = "Median Annual Social Security Benefit at Age 70",
       subtitle = "Among People with Social Security Benefits",
       x = "Income quintile",
       y = NULL) +
  remove_ticks() +
  remove_axis()   
```

@@

```{r, chart9}
read_csv("data/figure9.csv") %>%
filter(ncharts_reprate_payable %in% c("0-50%", "50-75%")) %>%
  filter(doby %in% cohorts) %>%
  group_by(doby) %>%
  summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>%
  ggplot(aes(doby, rep_rate_threshold)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::percent(rep_rate_threshold / 100)), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1))) +
  labs(title = "Age 70 Percentage of People Who fail to Replace 75% of Age 50-59 Earnings",
       subtitle = "Social Security benefits under payable law",
       x = "Birth cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()
```

>>>>

```{r rmarkdown-setup, echo = FALSE}
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)

knitr::opts_chunk$set(fig.width = 6.5, fig.height = 5)
```

@@

library(tidyverse)
library(urbnthemes)
library(grid)
library(gridExtra)
library(extrafont)

source("urban_style.R")

@@

chart1 <- read_csv("data/figure1.csv") %>%
  filter(ncharts_reprate %in% c("0-50%", "50-75%")) %>%
  filter(doby %in% cohorts) %>%
  group_by(doby) %>%
  summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>%
  ggplot(aes(doby, rep_rate_threshold)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::percent(rep_rate_threshold / 100)), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1))) +
  labs(x = "Birth cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

plotr(titler("Age 70 Percentage of People Who Fail to Replace 75% of Age 50-59 Earnings"),
      chart1,
      caption,
      sourcer("DYNASIM4"),
      heights = c(2, 30, 1, 1))
```

@@

```{r chart2}
chart2 <- read_csv("data/figure2.csv") %>%
  filter(doby %in% cohorts) %>%
  ggplot(aes(doby, ncharts_aftertax_income_P50)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::dollar(ncharts_aftertax_income_P50, largest_with_cents = 0)), 
            vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1))) +
  labs(x = "Birth cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

chart2 <- plotr(titler("Age-70, per-capita, price-adjusted income"),
      subtitler("Median shared annuitized income with imputed rent, other income, and taxes"),
      chart2,
      caption,
      sourcer("DYNASIM4"),
      heights = c(1.8, 1, 30, 1, 1))

ggsave("charts/chart2.pdf", 
       chart2,
       device = cairo_pdf(),
       width = 6.5,
       height = 5,
       units = "in")
```

@@

```{r chart3}
chart3 <- read_csv("data/figure3.csv") %>%
  filter(doby %in% cohorts) %>%
  ggplot(aes(doby, ncharts_aftertax_income_P50, fill = male)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::dollar(ncharts_aftertax_income_P50, largest_with_cents = 0)), 
            position = position_dodge(width = 0.7), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15))) +
  labs(x = "Birth cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

plotr(titler("Age-70, per-capita, price-adjusted, shared annuitized income with imputed rent, other income, and taxes"),
      subtitler("By sex"),
      chart3,
      caption,
      sourcer("DYNASIM4"),
      heights = c(2, 2, 30, 1, 1))
```

@@

```{r, chart3b}
chart3b <- read_csv("data/figure3b.csv") %>%
  filter(doby %in% cohorts) %>%
  ggplot(aes(doby, Ownssb_P50, fill = male)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::dollar(Ownssb_P50, largest_with_cents = 0)), 
            position = position_dodge(width = 0.75), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15))) +
  labs(x = "Birth cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

chart3 <- plotr(titler("Median Age-70 Price-Adjusted Social Security Benefits by Sex"),
      chart3b,
      caption,
      sourcer("DYNASIM4"),
      heights = c(2, 30, 1, 1))

ggsave("charts/chart3.pdf", 
       chart3,
       device = cairo_pdf(),
       width = 6.5,
       height = 5,
       units = "in")
```

@@

```{r chart4}
chart4 <- read_csv("data/figure4.csv") %>%
  filter(doby %in% cohorts) %>%
  filter(!is.na(male)) %>%
  ggplot(aes(doby, lifetime_earn_P50, fill = male)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::dollar(lifetime_earn_P50, largest_with_cents = 0)), 
            position = position_dodge(width = 0.9), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15))) +
  labs(x = "Birth cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

chart4 <- plotr(titler("Median Price-adjusted Earnings from Ages 25 to 69 at Age 70"),
      subtitler("By sex"),
      chart4,
      caption,
      sourcer("DYNASIM4"),
      heights = c(2, 2, 30, 1, 1))

ggsave("charts/chart4.pdf", 
       chart4,
       device = cairo_pdf(),
       width = 6.5,
       height = 5,
       units = "in")
```

@@

```{r chart5}
benefits <- c("Worker only", "Worker supplemented by\nspousal or survivor", "Spouse or survivor only")

chart5 <- read_csv("data/figure5.csv") %>%
  filter(doby %in% cohorts) %>%
  select(doby,
         `Worker supplemented by spousal or survivor` = dualben_Mean,
         `Worker only` = wrkonly_Mean,
         `Spouse or survivor only` = auxonly_Mean) %>%
  gather(key = "benefit_type", value = "share", -doby) %>%
  mutate(benefit_type = recode(benefit_type, 
                               `Worker supplemented by spousal or survivor` = "Worker supplemented by\nspousal or survivor")) %>%  
  mutate(benefit_type = factor(benefit_type, levels = benefits)) %>%
  ggplot(aes(benefit_type, share, fill = doby)) +
  geom_col(position = "dodge") +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1)), labels = scales::percent_format(accuracy = 1)) +
  labs(x = NULL,
       y = NULL) +
  remove_ticks()

chart5 <- plotr(titler("Social Security Benefit Type at Age 70 for Female Beneficiaries (%)"),
      chart5,
      caption,
      sourcer("DYNASIM4"),
      heights = c(2, 30, 1, 1))

ggsave("charts/chart5.pdf", 
       chart5,
       device = cairo_pdf(),
       width = 6.5,
       height = 5,
       units = "in")
```

@@

```{r chart6}
chart6 <- read_csv("data/figure6.csv") %>%
  filter(doby %in% cohorts) %>%
  filter(!is.na(raceeth)) %>%
  filter(raceeth != "4.Other") %>%
  ggplot(aes(doby, ncharts_aftertax_income_P50, fill = raceeth)) +
  geom_col(position = "dodge") +
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15)), 
                     labels = scales::dollar) +
  labs(x = "Birth cohort",
       y = NULL) +
  remove_ticks()

chart6 <- plotr(titler("Age-70, per-capita, price-adjusted, shared annuitized income\nwith imputed rent, other income, and taxes"),
      subtitler("By race and ethnicity"),
      chart6,
      caption,
      sourcer("DYNASIM4"),
      heights = c(5, 1, 30, 1, 1))

ggsave("charts/chart6.pdf", 
       chart6,
       device = cairo_pdf(),
       width = 6.5,
       height = 5,
       units = "in")
```

@@

```{r chart8}
chart8 <- read_csv("data/figure8.csv") %>%
  filter(doby %in% cohorts) %>%
  select(doby,
         `Scheduled law` = PCssb_P50,
         `Payable benefits` = PCssb_payable_P50) %>%
  gather(key = "Benefit type", value = "benefit", -doby) %>%
  mutate(`Benefit type` = factor(`Benefit type`, levels = c("Scheduled law", "Payable benefits"))) %>%
  ggplot(aes(doby, benefit, fill = `Benefit type`)) +
  geom_col(position = "dodge") +
  geom_text(mapping = aes(label = scales::dollar(benefit, largest_with_cents = 0)), 
            vjust = -1,
             position = position_dodge(width = 0.8)) +   
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.15)), 
                     labels = scales::dollar) +
  labs(x = "Income quintile",
       y = NULL) +
  remove_ticks() +
  remove_axis()

chart8 <- plotr(titler("Median Annual Social Security Benefit at Age 70"),
      subtitler("Among People with Social Security Benefits"),
      chart8,
      caption,
      sourcer("DYNASIM4"),
      heights = c(1.8, 1, 30, 1, 1))

ggsave("charts/chart8.pdf", 
       chart8,
       device = cairo_pdf(),
       width = 6.5,
       height = 5,
       units = "in")
```

@@

```{r, chart9}
chart9 <- read_csv("data/figure9.csv") %>%
filter(ncharts_reprate_payable %in% c("0-50%", "50-75%")) %>%
  filter(doby %in% cohorts) %>%
  group_by(doby) %>%
  summarize(rep_rate_threshold = sum(count_PctSum_10_count)) %>%
  ggplot(aes(doby, rep_rate_threshold)) +
  geom_col() +
  geom_text(mapping = aes(label = scales::percent(rep_rate_threshold / 100)), vjust = -1) +    
  scale_y_continuous(expand = expand_scale(mult = c(0, 0.1))) +
  labs(x = "Birth cohort",
       y = NULL) +
  remove_ticks() +
  remove_axis()

chart9 <- plotr(titler("Age 70 Percentage of People Who fail to Replace 75% of Age 50-59 Earnings"),
      subtitler("Social Security benefits under payable law"),
      chart9,
      caption,
      sourcer("DYNASIM4"),
      heights = c(1.8, 1, 30, 1, 1))

ggsave("charts/chart9.pdf", 
       chart9,
       device = cairo_pdf(),
       width = 6.5,
       height = 5,
       units = "in")
```
